Research Problem

### 2018-02-08 Segundo_Semestre/Seminario/Semana3/Presentacion.Rmd
version final

---
title: "Presentation"
author: "Mauricio Gonzalez"
date: "5/2/2018"
output:
  ioslides_presentation: default
  slidy_presentation: default
bibliography: /Users/MauricioGS1/INAOE/Segundo_Semestre/Propuesta/Bibliografia.bib
---

@@

## Fields involved
- Learning by interaction.
- Sequential Decision Making.
- Causal learning.

# Research Problem
## Statement
- Acquiring causal kwnoledge via interaction with the environment and using this knowledge to guide a decision-making process.

## Relevance
- Current RL methods are purely reactive.
- A lot of training time is required.
- Do not allow high-level reasoning.

@@

@@

* Reinforcement Learning
    + Google DeepMind (David Silver, Alex Graves, V. Mnih, Shanahan, Garnelo)
    + Oxford (Nando De Freitas, Shimon Whiteson)
    + Cambridge (Ghahramani)
    + Alberta University (Richard Sutton, Csaba Szepesvári)
    + UC Berkeley (Pieter Abbeel)
    + Carnegie Mellon (Salakhutdinov)
    + Imperial College (Murray Shanahan, Marta Garnelo)
    + University College London (Peter Dayan, Watkins, Dawid)

@@

## Outer Circle
Reference                  | Summary                                |
------------------------   |------------------------                |
[@holland1986statistics]   | General review of different views on Causality |
[@pearl1988probabilistic]  | Book on Networks for probabilistic reasoning|
[@heckerman1995decision] ||
[@spirtes2000causation]    | Classic General book on Causality      |
[@joyce1999foundations]    | Decision Theory and causal information |
[@pearl2009causality]      | Book on Causality and Graphical models |
[@koller2009probabilistic] | Book on Probabilistic Graphical Models |
[@lopez2015towards]        | Discriminative data-driven framework for distinguishing direction of causality |
[@goudet2017learning]      | Learning to generate data with neural networks |

@@

@@

Reference            | Summary                                                                      |
---------------------|------------------------------------------------------------------------------|
[@krynski2007role]   | 
[@danks2014unifying] | Cognitive functions can be modelled as operations on graphical models        |
[@lake2017building]  | Conditions for machines to be considered intelligent: Causal learning is one |

## Middle Circle
Reference | Summary |
----------|---------|
[@dawid2002influence] | Influence Diagrams|
[@eberhardt2008causal] ||
[@hagmayer2009decision] | |
[@meder2009role] | |
[@meder2010observing] | |
[@kemp2010learning] | |
[@wellen2012learning] | learning causal structure in local maner via precition-error loop |
[@eberhardt2012number] ||

@@

Reference | Summary |
----------|---------|
[@mnih2013playing] | Introducing Deep Q-Network |
[@silver2014deterministic] | Deterministic Policy Gradients |
[@mnih2015human] |  Nature report on Deep Q-Networks |
[@DBLP:journals/corr/SchulmanLMJA15] | Trust Region Policy Optimization |
[@DBLP:journals/corr/MnihBMGLHSK16] | Asynchronous Methods for Deep Reinforcement Learning |
[@van2016deep] ||
[@lakkarajuNIPS2016] ||
[@toulisNIPS2016] ||
[@kulkarniNIPS2016] | Hierarchical Deep Reinforcement Learning |
[@foersterNIPS2016] | Learning to Communicate with Deep Multi-Agent Reinforcement Learning |
[@lanctot2017] | Game-Theoretic Approach to Multiagent Reinforcement Learning  |
[@goudet2017learning] | Functional Causal Models with Generative Neural Networks |
[@rahmanian2017] | Online Dynamic Programming  |
[@louizos2017] |Causal Effect Inference with Deep Latent-Variable Models  |
[@christiano2017] |Deep Reinforcement Learning from Human Preferences|
[@o2016pgq] | Combining policy gradient and q-learning |
[@kirsch2017mdp | Environments |
[@zhang2017deeper] ||

## Inner Circle
Reference | Summary |
----------|---------|
[@hauser2012two] ||
[@hagmayer2013repeated] | How repeated decision making is guided by causal beliefs. |
[@ortega2014generalized] | Thompson sampling to solve sequential adaptive control when policy is known. |
[@alon2015online] | When feedback is specified by graph, the graph structure controls the difficulty of learning. |
[@bramley2015staying] ||
[@lattimoreNIPS2016] | Causal Bandits: Given a causal model, choose best intervention. |
[@albrecht2016exploiting] ||
[@garnelo2016towards] | Reinforcement Learning framework that builds symbolic representation of environment. |
[@innes2018reasoning] | An agent which, starting unaware of factors on which an optimal policy depends, learns optimal behaviour for single-stage decision problems via direct experience and advice from a domain expert.| 
[@pearl2018theoretical] ||

## End
- Thnks.

>>>>

---
title: "Research Problem"
author: "Mauricio Gonzalez"
date: "5/2/2018"
output:
  ioslides_presentation: default
  beamer_presentation: default
  slidy_presentation: default
bibliography: /Users/MauricioGS1/INAOE/Segundo_Semestre/Propuesta/Bibliografia.bib
---

@@

- The agent will interact with its environment and receive a feedback signal based on the actions taken by him, which will modify his cur- rent causal knowledge.
![action-feedback loop](/Users/MauricioGS1/INAOE/Primer_Semestre/Figures/cry.png)

- Before the next step is taken, the current causal knowledge will be taken into account when choosing the next action together with the current value of each posible action.
![action-feedback loop](/Users/MauricioGS1/INAOE/Primer_Semestre/Figures/baby.png)

- This new action and its outcome will again modify the causal knowl- edge, which will improve the next action and so on.
```{r fig.width=5, fig.height=5,echo=FALSE}
library(png)
library(grid)
img <- readPNG("/Users/MauricioGS1/INAOE/Primer_Semestre/Figures/Proposed.png")
grid.raster(img)
```

## Fields involved
- Learning by interaction.
- Sequential Decision Making.
- Causal learning.
- Bayesian inference.

# Research Problem
## Statement
- **Acquiring causal kwnoledge via interaction with the environment and using this knowledge to guide a decision-making process**
- Lay a bridge between Reinforcement Learning and Causal Learning: fundamental assumptions.
- Why reinforcement learning? Interventions are needed in order to acquire causal knowledge and RL provides an action-reaction interactive loop.

## Relevance
- Current RL methods are purely reactive.
- A lot of training time is required.
- Do not allow high-level reasoning.
- Learning causal structure will allow the agent to make better decisions because it will be able to consider consequences of his actions, and not only reacting to rewards.

@@

## Disclosure
- Causality as in [@pearl2009causality] and [@spirtes2000causation]
- Other definitions of Causality exist.

@@

* Reinforcement Learning
    + Google DeepMind (David Silver, Alex Graves, V. Mnih, Shanahan, Garnelo)
    + Oxford (Nando De Freitas, Shimon Whiteson)
    + Cambridge (Ghahramani)
    + Alberta University (Richard Sutton, Csaba Szepesvári)
    + UC Berkeley (Pieter Abbeel)
    + Carnegie Mellon (Salakhutdinov)
    + Imperial College (Murray Shanahan, Marta Garnelo)
    + University College London (Peter Dayan, Watkins, Dawid)
    + Edinburgh (Craig Innes)

@@

## Outer Circle
- Causality

Reference                  | Summary                                |
------------------------   |------------------------                |
[@holland1986statistics]   | General review of different views on Causality |
[@heckerman1995decision]   |Decision-theoretic foundations for causal reasoning  |
[@spirtes2000causation]    | Classic General book on Causality      |
[@joyce1999foundations]    | Decision Theory and causal information |
[@pearl2009causality]      | Book on Causality and Graphical models |
[@koller2009probabilistic] | Book on Probabilistic Graphical Models |

@@

- Reinforcement Learning

@@

- Cognitive aspects

Reference            | Summary                                                                      |
---------------------|------------------------------------------------------------------------------|
[@krynski2007role]   | The role of causality in judgment under uncertainty
[@danks2014unifying] | Cognitive functions can be modelled as operations on graphical models        |
[@lake2017building]  | Conditions for machines to be considered intelligent: Causal learning is one |

## Middle Circle
Reference | Summary |
----------|---------|
[@dawid2002influence] | Influence Diagrams|
[@eberhardt2008causal] |Causal discovery as a game vs Nature|
[@hagmayer2009decision] | Choices as interventions |
[@wellen2012learning] | learning causal structure in local maner via precition-error loop |

@@

Reference | Summary |
----------|---------|
[@mnih2013playing] | Introducing Deep Q-Network with Experience Replay |
[@silver2014deterministic] | Deterministic Policy Gradients |
[@lopez2015towards]        | Discriminative data-driven framework for distinguishing direction of causality |
[@DBLP:journals/corr/SchulmanLMJA15] | Trust Region Policy Optimization |
[@goudet2017learning] | Functional Causal Models with Generative Neural Networks |
[@o2016pgq] | Combining policy gradient and q-learning |

## Inner Circle
Reference | Summary |
----------|---------|
[@hagmayer2013repeated] | How repeated decision making is guided by causal beliefs. |
[@ortega2014generalized] | Thompson sampling to solve sequential adaptive control when policy is known. |
[@alon2015online] | When feedback is specified by graph, the graph structure controls the difficulty of learning. |
[@lattimoreNIPS2016] | Causal Bandits: Given a causal model, choose best intervention. |

Reference | Summary |
----------|---------|
[@albrecht2016exploiting] |Exploiting Causality for Selective Belief Filtering in Dynamic {B}ayesian Networks|
[@garnelo2016towards] | Reinforcement Learning framework that builds symbolic representation of environment. |
[@innes2018reasoning] | An agent which, starting unaware of factors on which an optimal policy depends, learns optimal behaviour for single-stage decision problems via direct experience and advice from a domain expert.| 
[@pearl2018theoretical] |Theoretical Impediments to Machine Learning With Seven Sparks from the Causal Revolution|
